\documentclass[%
  bachelor,%
  draft,%
  english,%
  ngerman,% last language set will be the main document language
  % accepted,%
  male,%
]{iswstud}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START external command definitions
% Tell LaTeX to create a list of indices
\makeindex
% Comes along with the glossaries package. Can be removed if you do not use
% glossaries anywhere in your document
\makeglossaries
% END external command definitions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START setting document properties
% Set author(s) names
\author{Daniel Koch}
% Short author names
\shortauthor{D.\@ Koch}
% Student's immatriculation number 
\immatriculationnumber{2948791}
% Place of birth of author
\placeofbirth{Leonberg}
% Your study major
\major{Mathematik}

% Set the date this document is printed/published
% Avoid typing in manually, either use `\today` or `\printdate{yyyy-mm-dd}`
\date{\today}


% Title of document
\title{Randwertprobleme mit gewichteter Kernkollokation}
% Define a short title if the main title is too long and truncated in parts of the document
%\shorttitle{Dies ist der Kurze Title meiner Arbeit}
% Theses can also have subtitles
%\subtitle{Unter Umst\"anden brauchen manche Abschlussarbeiten auch einen Untertitel}
% Define a partnering institute or company here (or multiple separated by `\and`)
\partner{IANS}

% Your examiner i.e., one of the professors of your thesis
\examiner{Prof. Dr. Bernard Haasdonk}
% Supervisor(s) of your thesis, multiple separated with `\and`
\supervisor{Prof. Dr. Bernard Haasdonk}
% END setting document properties
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START used defined content

% Put all your custom code (packages, styles, macros, etc.)

% This package is only included for demo purposes
%\usepackage[math]{blindtext}

% Add your bibliography file here.
\addbibresource{literature.bib}
%\addbibresource{/path/to/second/source.bib} % Import from multiple locations like this

% END user defined content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{mathtools}

\theoremstyle{plain}
\newtheorem{theorem}{Satz}[chapter]
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{example}[theorem]{Beispiel}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Bemerkung}


\newacronym[longplural={partielle Differentialgleichungen}]{PDE}{PDE}{partielle Differentialgleichung}
\newacronym{PD}{PD}{positiv definit}
\newacronym{SPD}{SPD}{strikt positiv definit}
\newacronym[longplural={reproduzierende Kern Hilberträume}]{RKHR}{RKHS}{reproduzierender Kern Hilbertraum}
\newacronym{LGS}{LGS}{lineares Gleichungssystem}
\newacronym{oBdA}{oBdA}{ohne Beschränkung der Allgemeinheit}
\newacronym{FEM}{FEM}{finite Elemente Methode}


\hyphenation{Hil-bert-raum Hil-bert-räu-me Di-rich-let Rand-be-ding-ung Kol-lo-ka-ti-on Kol-lo-ka-ti-ons-punk-te Kol-lo-ka-ti-ons-punk-ten}

\definecolor{mycolor1}{HTML}{e66101}%
\definecolor{mycolor2}{HTML}{5e3c99}%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% BEGIN document
\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START frontmatter
\frontmatter

%\coverpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START title page in main language
\maketitle
% END title page in main language
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START title page in other language
\begin{otherlanguage}{english}
  % Title of document in "otherlanguage"
  \title{Boundary Value Problems with Weighted Kernel Collocation}
  % Define a short title if the main title is too long and truncated in parts of the document  in "otherlanguage"
  \shorttitle{}
  % Theses can also have subtitles  in "otherlanguage"
  \subtitle{}
  % Define a partnering institute or company here (or multiple separated by `\and`)  in "otherlanguage"
  \partner{IANS}
  % Your study major in "otherlanguage"
  \major{Mathematik}

  \maketitle
\end{otherlanguage}
% END title page in other language
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\chapter*{Eigenständigkeitserklärung}
Hiermit erkläre ich, dass ich die vorliegende Bachelorarbeit selbstständig und nur unter Verwendung der angegebenen Literatur und Hilfsmittel angefertigt habe. Die aus
fremden Quellen direkt oder indirekt übernommenen Stellen sind als solche kenntlich
gemacht.
Die Arbeit ist weder in vollständig noch in wesentlichen Teilen Gegenstand
eines anderen Prüfungsverfahrens gewesen.
Das elektronische Exemplar stimmt mit den anderen Exemplaren überein.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START abstract in main language
\begin{abstract}
  %\Blindtext[3]
  In dieser Bachelorarbeit erweitern wir die Kernkollokation, ein Verfahren zur numerischen Lösung von partiellen Differentialgleichungen (\acs{PDE}s).\glsunset{PDE} Dafür nutzt die Kernkollokation einen interpolativen Ansatz, indem sie Ansatzfunktionen an verschiedenen Punkten im Inneren und auf dem Rand des Definitionsgebietes der \ac{PDE} ansetzt. 
  Aufgrund des diskreten Ansatzes werden die Randwerte der der numerischen Lösung \ac{PDE} nur an manchen Stellen exakt angenommen. Um zu erreichen, dass dies über den ganzen Rand der Fall ist, multiplizieren wir die Ansatzfunktionen mit einer Gewichtsfunktion und damit werden die Randbedingungen der \ac{PDE} automatisch erfüllt. Zusätzlich können wir dadurch die Ansatzpunkte auf dem Rand weglassen. Experimentell zeigt sich, dass die gewichtete Kernkollokation aber nur bedingt vernünftige Ergebnisse liefert, da es bei der Konstruktion der Gewichtsfunktionen für ein beliebiges Gebiet leicht passieren kann, dass in deren Ableitung Singularitäten entstehen, die zu schlechten Ergebnissen führen.
  \glsresetall
  \keywords{partielle Differentialgleichung \and Kern \and gewichtete Kernkollokation \and reproduzierende Kern Hilberträume}
\end{abstract}
% END abstract in main language
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START abstract in other language
\begin{otherlanguage}{english}
  \begin{abstract}
    %\Blindtext[3]
    In this bachelor's thesis, we extend the kernel collocation, a method to solve partial differential equations (\acs{PDE}s)\glsunset{PDE} numerically. The kernel collocation uses an interpolating approach by applying functions at different points on the boundary and the interior of the domain of a \ac{PDE}. Because of this discrete approach, the boundary values of the numerical solution are only exact in some places. To achieve an exact solution on the entire boundary, we multiply the interpolating functions by a weight function, which automatically fulfills the boundary conditions given by the \ac{PDE}. Additionally, we can omit the points on the boundary and don't need to apply any functions there. Experiments show that we only get reasonable results in some cases when using the weighted kernel collocation. When constructing the weight function for an arbitrary domain, it can easily happen that we get singularities in their derivatives, which causes bad results.
    \glsresetall
    %\draftname
       
    \keywords{partial differential equation \and kernel \and weighted kernel collocation \and reproducing kernel hilbertspace}
  \end{abstract}
\end{otherlanguage}
% END abstract in other language
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START lists of flaots


% Table of all contents
\tableofcontents

\printglossary
% List of all figures
\listoffigures

% List of all tables
\listoftables

% List of todos (only printed in non-final mode)
\listoftodos

% END list of floats
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START mainmatter
\mainmatter



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START actual document content
\include{chapters/einleitung}
\include{chapters/grundlagen}
\include{chapters/standard}
\include{chapters/gewichtet}
\include{chapters/implementation}
\include{chapters/numerischetests}
\include{chapters/schluss}
\include{chapters/anhang}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% START blind document
% THIS IS JUST SOME PLACEHOLDER BLINDDOCUMENT CODE. REMOVE BEFORE CREATING YOUR%
% DOCUMENT
%\input{blinddocument}
% END blind document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% END actual document content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% TODO: remove \nocite{*} for correct citation behavior
%\nocite{*}

\printbibliography


\end{document}
% END document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
